---
title: "Homework 1"
author: Emily Bamforth
output: github_document
---

This is my solution for Homework 1.

```{r}
library(tidyverse)
```

#### Problem 1

**Creating data frame with specified elements:**

```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "med", "high", "high", "low", "low",         "med", "high", "med", "med"))
  )
```

**Taking the mean of each variable:**

```{r prob1_means}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

**Findings:** We can take the mean of numbers and logical variables, but not the mean of character or factor variables.

**Apply `as.numeric` function to the logical, character, and factor variables.**

```{r prob1_numeric, eval = FALSE}
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

**Findings:**

* The logical variable is now numeric, with `TRUE` converted to 1 and `FALSE` converted to 0.

* The character variable could not be converted to a numeric variable. A vector of NAs was returned.

* The factor variable is now numeric, with `low` converted to 2, `medium` converted to 3, and `high` converted to 1.

* This indicates that R can coerce logical variables into numeric when taking a mean. Even though it can convert factor variables into numeric, it does not coerce them into numeric to take a mean.

**Transforming some more variables:**

```{r prob1_logical}

prob1_df %>% 
  pull(samp_gt_0) %>% 
  as.numeric() *
  pull(prob1_df, samp)

prob1_df %>% 
  pull(samp_gt_0) %>% 
  as.factor() *
  pull(prob1_df, samp)

prob1_df %>%
  pull(samp_gt_0) %>%
  as.factor() %>% 
  as.numeric() * 
  pull(prob1_df, samp)

```

#### Problem 2

```{r prob2_load}
data("penguins", package = "palmerpenguins")
```

**Describing the dataset:**

```{r prob2_row_col}
nrow(penguins)
ncol(penguins)
```

This dataset has 344 rows and 8 columns.

There are:

* Three factor variables:
`species` `island` and `sex`

* Three integer variables:
`flipper_length_mm` `body_mass_g` and `year`

* Two numeric variables:
`bill_length_mm` and `bill_depth_mm`

```{r prob2_summary}
summary(penguins)
```

The data was collected between 2007 and 2009 across three islands: `Bisco`, `Dream` and `Torgersen`.

There are three `species` represented: `Adelie` (n=152), `Chinstrap` (n=68), and `Gentoo` (n=124).

**Practicing manually calculating means:**

The mean `body_mass_g` of the sample:

```{r prob2_weight}
penguins %>% 
  pull(body_mass_g) %>%
  mean(na.rm = TRUE)
```

The mean `flipper_length_mm` of the sample:

```{r prob2_flipper}
penguins %>% 
  pull(flipper_length_mm) %>%
  mean(na.rm = TRUE)
```

The mean `bill_length_mm` of the sample:

```{r prob2_bill}
penguins %>% 
  pull(bill_length_mm) %>%
  mean(na.rm = TRUE)
```


**Make scatterplot:**
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point()

ggsave("penguins_scatter.pdf", height = 4, width = 6)
```










