---
title: "Homework 1"
author: Emily Bamforth
output: github_document
---

This is my solution for Homework 1.

```{r}
library(tidyverse)
```

## Problem 1

Create data frame with the specified elements.

```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "med", "high", "high", "low", "low",         "med", "high", "med", "med"))
  )
```

Take the mean of each variable in the data frame. What works and what doesn’t?

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

We can take the mean of numbers and logical variables, but not the mean of character or factor variables.

Apply `as.numeric` function to the logical, character, and factor variables.

```{r}
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

The logical variable is now numeric, with `TRUE` converted to 1 and `FALSE` converted to 0.

The character variable could not be converted to a numeric variable. A vector of NAs was returned.

The factor variable is now numeric, with `low` converted to `2`, `medium` converted to `3`, and `high` converted to `1`.

This indicates that R can coerce logical variables into numeric when taking a mean. Even though it can covert factor variables into numeric, it does not coerce them into numeric to take a mean.

```{r}

prob1_df %>% 
  pull(samp_gt_0) %>% 
  as.numeric() *
  pull(prob1_df, samp)

prob1_df %>% 
  pull(samp_gt_0) %>% 
  as.factor() *
  pull(prob1_df, samp)

prob1_df %>%
  pull(samp_gt_0) %>%
  as.factor() %>% 
  as.numeric() * 
  pull(prob1_df, samp)

```

## Problem 2

First installed the `penguins` package.

Describing the dataset:

```{r}
data("penguins", package = "palmerpenguins")

nrow(penguins)
ncol(penguins)
```

This dataframe has 344 rows and 8 columns.

Three factor variables:

`species` `island` and `sex`

Three integer variables:

`flipper_length_mm` `body_mass_g` and `year`

Two numeric variables:

`bill_length_mm` and `bill_depth_mm`








