---
title: "Homework 1"
author: Emily Bamforth
output: github_document
---

This is my solution for Homework 1.

```{r}
library(tidyverse)
```

## Problem 1

This problem is intended to emphasize variable types and introduce coercion; some awareness of how R treats numeric, character, and factor variables is necessary for working with these data types in practice.

Create a data frame with the specified elements.

```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "med", "high", "high", "low", "low",         "med", "high", "med", "med"))
  )
```

Try to take the mean of each variable in your dataframe. What works and what doesn’t?

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

We can take the mean of numbers and logical, but not the mean of character or factor.

In some cases, you can explicitly convert variables from one type to another. Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```

## Problem 2